Background on Patients

### 2023-05-05 Anxiety_Vis.Rmd
Adding Website to repo

---
title: "Anxiety_vis"
output: html_document
date: "2023-04-03"
---

@@

# Anxiety Treatment Progress Charts

```{r}
Mothership_Long <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]

@@

# Mothership_Mean_CUXOS20<-Mothership_Long20 %>%
#   group_by(TxDay) %>%
#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

```{r}
#Plot the Anxiety Mean for Full Sample
ggplot(data=Mothership_Mean_CUXOS,aes(x=TxDay,y=mean_CUXOS))+
  geom_line(size=1,color="red")+
  geom_point(color="red")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,40,by=5))+
  theme(panel.background=NULL)

ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20,by=1)) +
  labs(
    title="Quantity of discharges Per Treatment Day")+
  theme_classic()

### plot means based upon duration group membership

```{r}
#plot Anxiety mean with each group

# New dataset for the treatment duration Anxiety plot
Mothership_Mean_CUXOS<-Mothership_Long %>%
  group_by(Duration,TxDay) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
#delete weird Na values and put NA for values
Mothership_duration_CUXOS[6:20,3] = NA
Mothership_duration_CUXOS[37:41,3] = NA
Mothership_duration_CUXOS[74:83,3] = NA
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-21),]
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-41),]
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-61),]
Mothership_duration_CUXOS

@@

## Anxiety Treatment Progress by Characteristics

#### Race
```{r}

@@

Mothership_Mean_CUXOS_Race<-Mothership_Mean_CUXOS_Race[1:70,]
Mothership_Mean_CUXOS_Race
# plot
ggplot(data=subset(Mothership_Mean_CUXOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Anxiety Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(0,60,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E",
                              "gold3","#3E8300",
                              "#77B81C","darkorange2"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```
## GENDER IDENTITY
Create a New Data Set with an Average Anxiety Variable and Gender, then plot it
```{r}
#GENDER IDENTITY
#Create a New Data Set with an Average Anxiety Variable and Gender

@@

#### TREATMENT TRACK
```{r}
#Create a New Data Set with an Average Anxiety Variable and Track
Mothership_Mean_CUXOS_Track<-Mothership_Long_anx %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Treatment Track
ggplot(data=subset(Mothership_Mean_CUXOS_Track,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Treatment Track During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,46,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E","gold3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```
### EDUCATION
```{r}
#Create a New Data Set with an Average Anxiety Variable and Education
Mothership_Mean_CUXOS_Ed<-Mothership_Long_anx %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

### TREATMENT YEAR
```{r}
#Create a New Data Set with an Average Anxiety Variable and Year
Mothership_Mean_CUXOS_Year<-Mothership_Long_anx %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

>>>>

---
title: "Treatment Progression Visualizations"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

@@

The following code visualizes how patients scores on anxiety and depression measures change over the duration of treatment based upon sociodemographics and treatment information.

# Average Symptom Severity Treatment Progress Charts

## {.tabset}

### Create Data Frames
```{r}

Mothership_Long <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]

@@

# data frame by druation
Mothership_Mean_CUXOS_duration<-Mothership_Long %>%
  group_by(Duration,TxDay) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
Mothership_duration_CUXOS<-Mothership_Mean_CUXOS_duration[1:83,]

Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]

#Create a Time Variable
Mothership_Long$TxDay <- NA
Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20

#Create a New Data Set with an Average Anxiety Variable
Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

@@

### Anxiety
```{r}
#Plot the Anxiety Mean for Full Sample
ggplot(data=Mothership_Mean_CUXOS,aes(x=TxDay,y=mean_CUXOS))+
  geom_line(size=1,color="red")+
  geom_point(color="red")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,40,by=5))+
  theme(panel.background=NULL)
```

```{r,include=FALSE}
ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20,by=1)) +
  labs(
    title="Quantity of discharges Per Treatment Day")+
  theme_classic()
```

This visualization suggests that some patients get better quickly, while those that stay in treatment longer have higher anxiety.

#### Plot means based upon duration of treatment

```{r}
# New dataset for the treatment duration Anxiety plot
# Mothership_Mean_CUXOS<-Mothership_Long %>%
#   group_by(Duration,TxDay) %>%
#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
# 
# Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
#delete weird Na values and put NA for values
Mothership_duration_CUXOS[6:20,3] = NA
Mothership_duration_CUXOS[37:41,3] = NA
Mothership_duration_CUXOS[74:83,3] = NA
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-21),]
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-41),]
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-61),]
Mothership_duration_CUXOS

@@

This shows that those who are in treatment longer tend to have higher anxiety than those who are in treatment for less time.

### Depression

```{r}
#Plot the Depression Mean for Full Sample
ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
  geom_line(size=1,color="#0065A3")+
  geom_point(color="#0065A3")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
  theme(panel.background=NULL) 
```

#### Plot means based upon duration of treatment

```{r}
#plot depression mean with each group

# New dataset for the treatment duration depression plot
Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(Duration,TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

Mothership_duration_CUDOS<-Mothership_Mean_CUDOS[1:83,]
#delete weird Na values and put NA for values
Mothership_duration_CUDOS[6:20,3] = NA
Mothership_duration_CUDOS[37:41,3] = NA
Mothership_duration_CUDOS[74:83,3] = NA
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-21),]
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-41),]
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-61),]
Mothership_duration_CUDOS

ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  labs(subtitle = "Broken up by Discharge Date")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
  scale_color_manual(values=c("skyblue","#0065A3",
                              "navy","blue"))+
  theme(panel.background=NULL)
```

# Treatment Progress by Race

## {.tabset}

### Anxiety
```{r}

@@

Mothership_Mean_CUXOS_Race<-Mothership_Mean_CUXOS_Race[1:70,]
Mothership_Mean_CUXOS_Race
# plot
ggplot(data=subset(Mothership_Mean_CUXOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Anxiety Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(0,60,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E",
                              "gold3","#3E8300",
                              "#77B81C","darkorange2"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

### Depression
```{r}
Mothership_Long_dep <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long_dep <- Mothership_Long_dep[order(Mothership_Long_dep$ID1),]

#Create a Time Variable
Mothership_Long_dep$TxDay <- NA
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day1_CUDOS"]<-1
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day2_CUDOS"]<-2
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day3_CUDOS"]<-3
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day4_CUDOS"]<-4
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day5_CUDOS"]<-5
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day6_CUDOS"]<-6
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day7_CUDOS"]<-7
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day8_CUDOS"]<-8
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day9_CUDOS"]<-9
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day10_CUDOS"]<-10

#Overall race
Mothership_Mean_CUDOS_Race<-Mothership_Long_dep %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
# plot
ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","darkgreen",
                              "#0098DB","#0065A3","#A0AFA1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","lightgrey","lightgrey",
                              "lightgrey","lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("lightgrey","lightgrey","darkgreen",
                              "lightgrey","#0065A3","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

# Treatment Progress by Gender Idenitity

## {.tabset}

### Anxiety
```{r}
#GENDER IDENTITY
#Create a New Data Set with an Average Anxiety Variable and Gender

@@

### Depression
```{r}
#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

Mothership_Mean_CUDOS_Gender <-filter(Mothership_Mean_CUDOS_Gender,
                                      Gender_1 != "Unknown",
                                      Gender_1 != "Non-Binary",
                                      Gender_1 != "Other"
                                        )
#Create the Depression Line Graph by Gender
ggplot(data=subset(Mothership_Mean_CUDOS_Gender,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Gender During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(15,45,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

# Treatment Progress by Treatment Track

## {.tabset}

### Anxiety
```{r}
#Create a New Data Set with an Average Anxiety Variable and Track
Mothership_Mean_CUXOS_Track<-Mothership_Long_anx %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Treatment Track
ggplot(data=subset(Mothership_Mean_CUXOS_Track,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Treatment Track During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,46,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E","gold3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

### Depression
```{r}
#Create a New Data Set with an Average Depression Variable and Track
Mothership_Mean_CUDOS_Track<-Mothership_Long_dep %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

#Create the Depression Line Graph by Treatment Track
ggplot(data=subset(Mothership_Mean_CUDOS_Track,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Track During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

# Treatment progress by Education

## {.tabset}

### Anxiety
```{r}
#Create a New Data Set with an Average Anxiety Variable and Education
Mothership_Mean_CUXOS_Ed<-Mothership_Long_anx %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

### Depression
```{r}
#Create a New Data Set with an Average Depression Variable and Education
Mothership_Mean_CUDOS_Ed<-Mothership_Long_dep %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

#Create the Depression Line Graph by Education
ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.75)+
  geom_point(size=.75)+
  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.75)+
  geom_point(size=.75)+
  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
  scale_color_manual(values=c("#209845","lightgrey","lightgrey",
                              "#0098DB","lightgrey","lightgrey",
                              "lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

# Treatment Progress by Treatment Year

## {.tabset}

### Anxiety
```{r}
#Create a New Data Set with an Average Anxiety Variable and Year
Mothership_Mean_CUXOS_Year<-Mothership_Long_anx %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

@@

### Depresssion

```{r}
#Create a New Data Set with an Average Depression Variable and Year
Mothership_Mean_CUDOS_Year<-Mothership_Long_dep %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

str(Mothership_Long_dep$TxYear)

#Create the Depression Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#91A9F1","darkgreen",
                              "#0065A3","#7F8559","#4B5D8E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

#Create the Depression Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("lightgrey","lightgrey","lightgrey",
                              "lightgrey","lightgrey","lightgrey",
                              "#0065A3","lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

### 2023-05-05 Data_Import.Rmd
Adding Website to repo

---
title: "Data_Import"
output: html_document
date: "2023-04-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

## Import data

@@

# Background Statistics
```{r}
### Bar Chart for Discharge Status ###
plot(Mothership2$DC_status_1)

ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
  geom_bar(color = "black",fill="darkgreen")+
  ggtitle("Frequency of Treatment Discharge Status") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Discharge Status") +
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6000))

### Bar Chart for Education Status ###

ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))

### Bar chart for race ###
ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
  geom_bar(color = "black",fill="darkblue")+
  ggtitle("Frequency of Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Race")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

### Bar chart for gender###
ggplot(data = subset(Mothership, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
  geom_bar(color = "black",fill="darkorange")+
  ggtitle("Frequency of Gender") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Gender")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

### Treatment Track ###

ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

### Treatment Year ###

Mothership$TxYear

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1500))

### Duration of Treatment ###
ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
  geom_bar(color = "black",fill="lightgreen")+
  ggtitle("Frequency of Patients per Duration of Treatment") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Duration")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

## Pie Chart For Education Status 
```{r}
#Create Table and Data Frame
Education<-table(Mothership$Education_1)
Education_df<-as.data.frame(Education)
Education_df

@@

>>>>

---
title: "Background on Patients"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)

@@

# Import data

@@

# Sociodemographic Visualizations

## {.tabset}

### Education Status
```{r}
ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))
```

### Race
```{r}
ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
  geom_bar(color = "black",fill="darkblue")+
  ggtitle("Frequency of Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Race")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

### Gender
```{r}
ggplot(data = subset(Mothership, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
  geom_bar(color = "black",fill="darkorange")+
  ggtitle("Frequency of Gender") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Gender")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

# Pie Chart For Education Status 
We wanted to learn how to make a pie chart in R so here is one!
```{r}
#Create Table and Data Frame
Education<-table(Mothership$Education_1)
Education_df<-as.data.frame(Education)
Education_df

@@

# Treatment Related Visualizations

## {.tabset}

### Discharge Status
```{r}
### Bar Chart for Discharge Status ###

ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
  geom_bar(color = "black",fill="darkgreen")+
  ggtitle("Frequency of Treatment Discharge Status") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Discharge Status") +
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6000))
```

### Treatment Track
```{r}
### Treatment Track ###

ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

### Treatment Year
```{r}
### Treatment Year ###

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1500))
```

### Duration of Treatment
```{r}
### Duration of Treatment ###
ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
  geom_bar(color = "black",fill="lightgreen")+
  ggtitle("Frequency of Patients per Duration of Treatment") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Duration")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
